\singlespacing{\textbf{Efficient Pollution Abatement in Electricity Markets with Intermittent Renewable Energy}}

### 2020-01-02 documents/revision.tex
Update revision
- add difference file
- minor changes to introduction, model, and formatting

\documentclass[11pt,a4paper,leqno]{extarticle}
\usepackage[margin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{booktabs} % for toprule, midrule and bottomrule
\usepackage{adjustbox}
\usepackage{amsmath}
\usepackage{bbold}
\usepackage{etoolbox}
\usepackage{setspace} % for \onehalfspacing and \singlespacing macros
\usepackage[hidelinks]{hyperref}
\usepackage{array}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{caption}
\usepackage{pdflscape}
\usepackage{caption}
\usepackage{tabularx}
\usepackage{authblk}
\usepackage{float}
\usepackage{siunitx}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage[authoryear]{natbib}
\usepackage{scrextend}
\usepackage{nicefrac}
\usepackage{enumitem}
\usepackage{multirow}
\usepackage{xcolor}
\usepackage{cleveref}
\usepackage{varwidth}
\usepackage{gensymb}

@@

@@

	Our results quantify the relationship between the intertemporal elasticity of substitution for electricity consumption  (IES) and the elasticity of substitution between renewable and fossil energy. The intuition behind the relationship is based on how the IES affects the desire for smoother consumption. When the IES is low, consumers want their electricity consumption to be smooth; so, they prefer not to consume intermittent sources of energy such as solar. This means that the substitutability between renewables and fossils will be small. On the other hand, when the IES is high, consumers care less about smoothing their electricity consumption, so they are more willing to substitute between renewable and fossil energy. In short, the elasticity of substitution between renewable and fossil energy increases with the IES. We also find that the elasticity of substitution between renewable and fossil energy is not a simple, constant relationship. This is important because a significant amount of literature has assumed a CES structure between renewable and fossil energy (see \citet{Pap}); this assumption has been motivated, in part, by the need to capture imperfect substitutability between these two generation technologies as a result of intermittency. But, our model finds that the elasticity of substitution between renewable and fossil energy is far from constant as a consequence of intermittency. This elasticity appears to vary with the quantity of each energy technology. Hence, we argue against assuming a CES structure. Alternatively, we find that a variable elasticity of substitution (VES) production function can be used to approximate the relationship that our model finds between the elasticity of substitution and the quantities of each technology.\footnote{ The VES production function was created by \citet{VES}; we describe it in further detail in the \hyperref[sec:VES]{discussion}. } The numerical results suggest this relationship is roughly linear which is exactly what a VES function assumes. Moreover, a VES function is analytically tractable, so it can be implemented in other frameworks without making them overly complicated.

@@

	Consumers purchase a quantity of electricity $Z_t$ in each period $t$. Furthermore, they demand a greater quantity of electricity in certain periods; for instance, consumers need more electricity during the middle of the day more than at night. At the same time, consumers are willing to shift their consumption from one period to another in response to a shift in prices. Overall, these characteristics can be captured using a standard CES utility function.  Furthermore, since CES preferences are homothetic, we may aggregate the consumers into a single representative consumer. This consumer has the utility function
	\begin{equation}
	U = \left( \sum_t \alpha_t Z_t^\phi  \right)^{1/\phi} \qquad \phi < 1
	\end{equation}
	where $\sigma = 1/(1-\phi)$ is the intertemporal elasticity of substitution for electricity consumption. The restriction on $\phi$ implies we have  $\sigma > 0$; additionally, since electricity consumption increases utility, we must have $\alpha_t > 0$ for all $t$.  For simplicity, we also define $\sum_t \alpha_t = 1$, so that a 1\% increase in electricity consumption in all periods increases utility by 1\%; consequently, we then have $\alpha_t \in (0,1)$. The budget constraint is given by
	\begin{equation}
	I = \sum_t p_t Z_t
	\end{equation}
	where $p_t$ is the price of electricity in period $t$ and $I$ is the income. Our representative consumer maximizes utility against this budget constraint; the first order conditions of this problem imply:
	\begin{align}\label{eq:demand}
	Z_t &= \left(\frac{\alpha_t}{p_t} \right)^\sigma \frac{I}{P} \\\label{eq:priceindex}
	P &= \sum_t \alpha_t^\sigma p_t^{1-\sigma}
	\end{align}
	where $P$ is the price index. Note that this model naturally does not allow for blackouts in equilibrium, since the price of electricity in any period gets arbitrarily large as the quantity of energy consumed in that period approaches 0. Furthermore, note that prices must be positive; although this is sometimes violated in reality, we do not believe that this assumption significantly affects our analysis.

@@

	We let $X_i$  represent the quantity of energy technology $i$ , and we define its output per unit in period $t$ as $\xi_{1,t}$. So, for example, if $i$ is solar power, $X_i$ would be the number of solar panels and $\xi_{i,t}$ may be kWh generated per solar panel in period $t$. Consequently, the energy generated in period $t$, $Z_t$, is given by $\sum_i \xi_{i,t} X_i$. To simplify notation, we have
	\begin{align}
	\mathbf{X} \equiv \begin{pmatrix}
	X_1\\
	\vdots\\
	X_n
	\end{pmatrix} ,\;
	\mathbf{Z} \equiv \begin{pmatrix}
	Z_1\\
	\vdots\\
	Z_m
	\end{pmatrix} ,\;
	\mathbf{p} \equiv \begin{pmatrix}
	p_1\\
	\vdots\\
	p_m
	\end{pmatrix} ,\;
	\boldsymbol{\xi} \equiv \begin{pmatrix}
	\xi_{1,1} & \dots & \xi_{1,m}\\
	\vdots & \ddots & \\
	\xi_{n,1} &  & \xi_{n,m}
	\end{pmatrix} 
	\end{align}
	where we have $n$ technologies, $m$ periods, and $\mathbf{Z} \equiv \boldsymbol{\xi}^T \mathbf{X}$. A key element of this model is that $\mathbf{X}$ does not vary by time. This is important because the time scale of our model must be fairly granular to study the effects of intermittency. So, for instance, we may have $t \in \{ 1, \dots, 24\}$ representing each hour of the day. Over such short time scales, the intermittency of renewables like solar and wind can significantly affect their economic value. Additionally, this allows us to assume that producers cannot modify the quantity of the technologies they deploy. And, thirdly, for certain technologies, this time frame is short enough to assume that $\boldsymbol{\xi}$ is exogenous; that is, technologies like coal power cannot significantly modify their output within a day, so $\boldsymbol{\xi}$ can be treated as a given set of constants. These latter two assumptions, that $\mathbf{X}$ cannot change over time and that $\boldsymbol{\xi}$ is exogenous, are important for parsimony, because they prevent more complicated dynamics from entering our model. So, by assuming a sufficiently short time frame, we can continue our study of intermittency in a relatively simpler setting. Furthermore, in this setting, we can use ``intermittent'' to refer to a technology where output per unit, $\xi_{i,t}$, varies over time (with $t$).

	Next, our representative firm sets $\mathbf{X}$ once to maximize total profit; it does so by setting marginal profit equal to marginal cost.  \citet{HH} note that past literature has argued for concave cost functions in the energy market due to effects such as economies of scale and learning-by-doing; on the other hand, standard cost functions are generally convex. So, like Helm and Meir, we take an intermediate approach by using a linear cost function. Specifically, the total cost of the input bundle $\mathbf{X}$ is given by $ \sum_i c_i X_i \equiv \mathbf{c}^T \mathbf{X}$ where $c_i$ is the cost per unit of $X_i$. Total profit is given by 
	\begin{equation}
	\Pi = \mathbf{p}^T \mathbf{Z} - \mathbf{c}^T \mathbf{X}
	\end{equation}
	To simplify the algebra, we set the number of technologies equal to the number of periods $(n=m)$. Additionally, we further require that the output per unit of each technology is unique and non-negative in each period; in other words, the output per unit of one technology is not a linear combination of those of the other technologies in our set. This then implies that $\boldsymbol{\xi}$ is of full rank and therefore invertible.  Now, maximizing profit, we find the first order condition:
	\begin{equation}\label{eq:firm_foc}
	\frac{\partial \Pi}{\partial \mathbf{X}} = 0 \implies \mathbf{p} =  \boldsymbol{\xi}^{-1} \mathbf{c}
	\end{equation}
	Combining this FOC with the demand equation (\autoref{eq:demand}) allows us to find the equilibrium. Generally, the equilibrium results for any number of technologies ($n$) are analytic, but they are difficult to interpret algebraically due to the number of parameters involved.

@@

	For more tractable results, we consider a simpler scenario where $n = m = 2$ and $\sigma = 1$ (Cobb-Douglas); this particular case is described in greater details in \hyperref[sec:cobbdoug]{Appendix A.A}. These assumptions simplify the discussion of intermittency. In a two-period, two-technology model, we can intuit that the magnitude of intermittency is given by how much $\xi_{i,t}/c_i$ (output per dollar) varies with $t$; this is useful for understanding the link between intermittency and other parameters like $\sigma$. Furthermore, as we will discuss in our \hyperref[sec:results]{results}, assuming $\sigma=1$ is not far from its empirical estimate.

@@

	Furthermore, since only total electricity output weighted by $\boldsymbol{\alpha}$ matters when choosing the optimal set of inputs, there is no preference for smoothing electricity consumption over time; again, this is because $\sigma \to \infty$ corresponds to the case of perfect substitutes. Consequently, the intermittency of an input has no effect on its adoption. This makes different inputs stronger substitutes for one another. To better understand why, suppose we have two technologies that cost the same per unit and produce the same total amount of electricity; one technology only produces during peak hours and the other producers only during the off-peak. If we have $\alpha_{peak} = \alpha_{off-peak}$, both technologies are perfect substitutes for one another when $\sigma \to \infty$. This is because any feasible combination of the technologies would give the same utility to the representative consumer. For instance, using the first technology and only getting electricity during peak hours would offer the same amount of utility as using a mix of both technologies and getting electricity during both periods. On the other hand, if we had finite $\sigma$, consumers would care about having electricity during both periods. This would cause the equilibrium solution to involve using both inputs. So, in general, when $\sigma \to \infty$, intermittency does not matter and inputs are more substitutable.

@@

	The second approach is to use a variable elasticity of substitution function to model the relationship between clean and dirty energy.  A VES function would approximately capture the dynamics of $e$, the elasticity of substitution between clean and dirty technology,  while keeping a theoretical model relatively simple. The latter is because assuming a VES structure between clean and dirty energy only requires considering one more parameter than a traditional CES function. To be more precise, the VES function is defined in \citet{VES} as
	\begin{align}
	Z &= \gamma X_1^{\omega(1-\delta \rho)} \left( X_2 + (\rho - 1) X_1 \right)^{\omega \delta \rho} \\
	e &= 1 + \beta (X_1 / X_2) \\
	\beta &= (\rho - 1) / ( 1- \delta \rho ) 
	\end{align}
	\vspace{-4ex}
	$$\gamma > 0, \quad \omega > 0, \quad0 < \delta < 1, \quad 0 \leq \delta \rho \leq 1 , \quad (X_2/X_1) >  -\beta $$
	where $\omega, \delta, \rho$, and $\gamma$ are parameters, $Z$ is the output, $X_1$ and $X_2$ are the inputs, and $e$ is the elasticity of substitution between $X_1$ and $X_2$. In the context of an electricity sector, we can think of $Z$ as electricity output while $X_1$ and $X_2$ represent dirty and clean inputs. Note that $e$ is a linear function of $X_1/X_2$; this relationship allows a VES function to approximate the effects of intermittency. To show why, we plot $e$ against its VES approximation $\hat{e}$ for solar and coal in \autoref{fig:ves}. This approximation was fit by running OLS against the numerical results for $e$ while holding the intercept fixed at 1.\footnote{ There also exists a VES function described by \citet{VES} with the form $e = \beta_0 + \beta (X_1/X_2)$. This function may provide a better approximation of $e$, but there is no tractable production function that underlies it for $\beta_0 \neq 1$. Hence, we only consider the case where $\beta_0 = 1$, since the entire point of taking a VES approximation, in this case, is for analytical tractability. } We can see that, as either the capacity of solar or coal dominates the market, the approximation becomes weaker. But, overall, it seems to mimic the shape of the true elasticity of substitution $e$ implied by our model of intermittency. Hence, a  VES function is a reasonable alternative to a CES function -- it better models intermittency while also maintaining parsimony.

>>>>

\documentclass[11pt,a4paper,leqno]{extarticle}
\usepackage[margin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{booktabs} % for toprule, midrule and bottomrule
\usepackage{adjustbox}
\usepackage{amsmath}
\usepackage{bbold}
\usepackage{etoolbox}
\usepackage{setspace} % for \onehalfspacing and \singlespacing macros
\usepackage[hidelinks]{hyperref}
\usepackage{array}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{caption}
\usepackage{pdflscape}
\usepackage{caption}
\usepackage{tabularx}
\usepackage{authblk}
\usepackage{float}
\usepackage{siunitx}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage[authoryear]{natbib}
\usepackage{scrextend}
\usepackage{nicefrac}
\usepackage{enumitem}
\usepackage{multirow}
\usepackage{xcolor}
\usepackage{cleveref}
\usepackage{varwidth}
\usepackage{gensymb}
\usepackage{lineno}

@@

% line numbers
\linenumbers

@@

	Our results quantify the relationship between the intertemporal elasticity of substitution for electricity consumption  (IES) and the elasticity of substitution between renewable and fossil energy. The intuition behind the relationship is based on how the IES affects the desire for smoother consumption. When the IES is low, consumers want their electricity consumption to be smooth; so, they prefer not to consume intermittent sources of energy such as solar. This means that the substitutability between renewables and fossils will be small. On the other hand, when the IES is high, consumers care less about smoothing their electricity consumption, so they are more willing to substitute between renewable and fossil energy. In short, the elasticity of substitution between renewable and fossil energy increases with the IES.

	Furthermore, our numerical results show that the elasticity of substitution between renewable and fossil energy is non-constant and rises with the intermittency of present electricity generation. This occurs because consumers prefer to smooth their electricity consumption; so, when electricity output varies more over time, it becomes harder to replace consistent technologies with intermittent technologies. The result that the elasticity of substitution between technologies is non-constant is important because a significant amount of literature has assumed a CES structure between renewable and fossil energy (see \citet{Pap}); this assumption has been motivated, in part, by the need to capture imperfect substitutability between these two generation technologies as a result of intermittency. But, our model finds that intermittency itself causes a non-constant elasticity between technologies. This elasticity appears to vary with the cost of each energy technology. Hence, we argue against assuming a CES structure. Alternatively, we find that a variable elasticity of substitution (VES) production function can be used to approximate the relationship that our model finds between the elasticity of substitution and the quantities of each technology.\footnote{ The VES production function was created by \citet{VES}; we describe it in further detail in the \hyperref[sec:VES]{discussion}. } The numerical results suggest this relationship is roughly linear which is exactly what a VES function assumes. Moreover, a VES function is analytically tractable, so it can be implemented in other frameworks without making them overly complicated.

@@

	Consumers purchase a quantity of electricity $Z_t$ in each period $t$. Furthermore, they demand a greater quantity of electricity in certain periods; for instance, consumers need more electricity during the middle of the day more than at night. At the same time, consumers are willing to shift their consumption from one period to another in response to a shift in prices. Overall, these characteristics can be captured using a standard CES utility function.  Hence, we consider a representative consumer with the utility function
	\begin{equation}
	U = \left( \sum_t \alpha_t Z_t^\phi  \right)^{1/\phi} \qquad \phi < 1
	\end{equation}
	where $\sigma = 1/(1-\phi)$ is the intertemporal elasticity of substitution for electricity consumption. The restriction on $\phi$ implies we have  $\sigma > 0$; additionally, since electricity consumption increases utility, we must have $\alpha_t > 0$ for all $t$.  For simplicity, we also define $\sum_t \alpha_t = 1$, so that a 1\% increase in electricity consumption in all periods increases utility by 1\%; consequently, we then have $\alpha_t \in (0,1)$. The budget constraint is given by
	\begin{equation}
	I = \sum_t p_t Z_t
	\end{equation}
	where $p_t$ is the price of electricity in period $t$ and $I$ is the income. Our representative consumer maximizes utility against this budget constraint; the first order conditions of this problem imply:
	\begin{align}\label{eq:demand}
	Z_t &= \left(\frac{\alpha_t}{p_t} \right)^\sigma \frac{I}{P} \\\label{eq:priceindex}
	P &= \sum_t \alpha_t^\sigma p_t^{1-\sigma}
	\end{align}
	where $P$ is the price index. Note that this model naturally does not allow for blackouts in equilibrium, since the price of electricity in any period gets arbitrarily large as the quantity of energy consumed in that period approaches 0. Furthermore, note that prices must be positive; although this is sometimes violated in reality, we do not believe that this assumption significantly affects our analysis.

@@

	We let $X_i$  represent the quantity of energy technology $i$ , and we define its output per unit in period $t$ as $\xi_{1,t}$. So, for example, if $i$ is solar power, $X_i$ would be the number of solar panels and $\xi_{i,t}$ may be kWh generated per solar panel in period $t$. Consequently, the energy generated in period $t$, $Z_t$, is given by $\sum_i \xi_{i,t} X_i$. To simplify notation, we have
	\begin{align}
	\mathbf{X} \equiv \begin{pmatrix}
	X_1\\
	\vdots\\
	X_n
	\end{pmatrix} ,\;
	\mathbf{Z} \equiv \begin{pmatrix}
	Z_1\\
	\vdots\\
	Z_m
	\end{pmatrix} ,\;
	\mathbf{p} \equiv \begin{pmatrix}
	p_1\\
	\vdots\\
	p_m
	\end{pmatrix} ,\;
	\boldsymbol{\xi} \equiv \begin{pmatrix}
	\xi_{1,1} & \dots & \xi_{1,m}\\
	\vdots & \ddots & \\
	\xi_{n,1} &  & \xi_{n,m}
	\end{pmatrix} 
	\end{align}
	where we have $n$ technologies, $m$ periods, and $\mathbf{Z} \equiv \boldsymbol{\xi}^T \mathbf{X}$.

	A key assumption of our model is that the time scale is short enough such that the input vector $\mathbf{X}$ does not vary with time and the output per unit matrix $\boldsymbol{\xi}$ is exogenous. This is important because the time scale of our model must be fairly granular to study the effects of intermittency. So, for instance, a reasonably short two-period setting would be $t \in$ \{peak, off-peak\}. Since the overall time frame is a single day, producers cannot modify the quantity of the technologies they deploy, so $\mathbf{X}$ must be fixed. Furthermore, this time frame is short enough to assume that $\boldsymbol{\xi}$ is exogenous; that is, technologies like coal power cannot significantly modify their output within a day, so $\boldsymbol{\xi}$ can be treated as a given set of constants.  These two implications, that $\mathbf{X}$ cannot change over time and that $\boldsymbol{\xi}$ is exogenous, are important for parsimony, because they prevent more complicated dynamics from entering our model. And, they also make intermittency economically relevant, because having $\mathbf{X}$ fixed and $\boldsymbol{\xi}$ exogenous means that producers have no way of compensating for intermittent output; therefore, they must view the intermittency of technologies like solar and wind as a trade-off.

	Furthermore, assuming a short time scale makes it simple to differentiate intermittent technologies. In this setting, we can use ``intermittent'' to refer to a technology where  output per unit, $\xi_{i,t}$, varies over time (with $t$).  This is because we define intermittency as variation in electricity output over time due to physical constraints. Based on our assumptions, the only source of variation in output over time comes from $\boldsymbol{\xi}$. Hence, we only need to consider $\boldsymbol{\xi}$ to determine which inputs are intermittent.

	Now, we consider the firm's problem. Our representative firm chooses $\mathbf{X}$ to maximize total profit; it does so by setting marginal profit equal to marginal cost.  \citet{HH} note that past literature has argued for concave cost functions in the energy market due to effects such as economies of scale and learning-by-doing; on the other hand, standard cost functions are generally convex. So, like Helm and Meir, we take an intermediate approach by using a linear cost function. Specifically, the total cost of the input bundle $\mathbf{X}$ is given by $ \sum_i c_i X_i \equiv \mathbf{c}^T \mathbf{X}$ where $c_i$ is the cost per unit of $X_i$. Then, total profit is given by 
	\begin{equation}
	\Pi = \mathbf{p}^T \mathbf{Z} - \mathbf{c}^T \mathbf{X}
	\end{equation}
	To simplify the algebra, we set the number of technologies equal to the number of periods $(n=m)$. Additionally, we further require that the output per unit of each technology is unique and non-negative in each period; in other words, the output per unit of one technology is not a linear combination of those of the other technologies in our set. This then implies that $\boldsymbol{\xi}$ is of full rank and therefore invertible.  Now, maximizing profit, we find the first order condition:
	\begin{equation}\label{eq:firm_foc}
	\frac{\partial \Pi}{\partial \mathbf{X}} = 0 \implies \mathbf{p} =  \boldsymbol{\xi}^{-1} \mathbf{c}
	\end{equation}
	Combining this FOC with the demand equation (\autoref{eq:demand}) allows us to find the equilibrium. Generally, the equilibrium results for any number of technologies ($n$) are analytic, but they are difficult to interpret algebraically due to the number of parameters involved.

@@

	For more tractable results, we consider a simpler scenario where $n = m = 2$ and $\sigma = 1$ (Cobb-Douglas); this particular case is described in greater detail in \hyperref[sec:cobbdoug]{Appendix A.A}. These assumptions simplify the discussion of intermittency. In a two-period, two-technology model, we can intuit that the magnitude of intermittency is given by how much $\xi_{i,t}/c_i$ (output per dollar) varies with $t$; this is useful for understanding the link between intermittency and other parameters like $\sigma$. Furthermore, as we will discuss in our \hyperref[sec:results]{results}, assuming $\sigma=1$ is not far from its empirical estimate.

@@

	Furthermore, since only total electricity output weighted by $\boldsymbol{\alpha}$ matters when choosing the optimal set of inputs, there is no preference for smoothing electricity consumption over time; again, this is because $\sigma \to \infty$ corresponds to the case of perfect substitutes. Consequently, the intermittency of an input has no effect on its adoption. This makes different inputs stronger substitutes for one another. To better understand why, suppose we have two technologies that cost the same per unit and produce the same total amount of electricity; one technology only produces during peak hours and the other producers only during the off-peak. If we have $\alpha_{\text{peak}} = \alpha_{\text{off-peak}}$, both technologies are perfect substitutes for one another when $\sigma \to \infty$. This is because any feasible combination of the technologies would give the same utility to the representative consumer. For instance, using the first technology and only getting electricity during peak hours would offer the same amount of utility as using a mix of both technologies and getting electricity during both periods. On the other hand, if we had finite $\sigma$, consumers would care about having electricity during both periods. This would cause the equilibrium solution to involve using both inputs. So, in general, when $\sigma \to \infty$, intermittency does not matter and inputs are more substitutable.

@@

	The second approach is to use a variable elasticity of substitution function to model the relationship between clean and dirty energy.  A VES function would approximately capture the dynamics of $e$, the elasticity of substitution between clean and dirty technology,  while keeping a theoretical model relatively simple. The latter is because assuming a VES structure between clean and dirty energy only requires considering one more parameter than a traditional CES function. To be more precise, the VES function is defined in \citet{VES} as
	\begin{align}
	Z &= \gamma X_1^{\omega(1-\delta \rho)} \left( X_2 + (\rho - 1) X_1 \right)^{\omega \delta \rho} \\
	e &= 1 + \beta (X_1 / X_2) \\
	\beta &= (\rho - 1) / ( 1- \delta \rho ) 
	\end{align}
	$$\gamma > 0, \quad \omega > 0, \quad0 < \delta < 1, \quad 0 \leq \delta \rho \leq 1 , \quad (X_2/X_1) >  -\beta $$
	where $\omega, \delta, \rho$, and $\gamma$ are parameters, $Z$ is the output, $X_1$ and $X_2$ are the inputs, and $e$ is the elasticity of substitution between $X_1$ and $X_2$. In the context of an electricity sector, we can think of $Z$ as electricity output while $X_1$ and $X_2$ represent dirty and clean inputs. Note that $e$ is a linear function of $X_1/X_2$; this relationship allows a VES function to approximate the effects of intermittency. To show why, we plot $e$ against its VES approximation $\hat{e}$ for solar and coal in \autoref{fig:ves}. This approximation was fit by running OLS against the numerical results for $e$ while holding the intercept fixed at 1.\footnote{ There also exists a VES function described by \citet{VES} with the form $e = \beta_0 + \beta (X_1/X_2)$. This function may provide a better approximation of $e$, but there is no tractable production function that underlies it for $\beta_0 \neq 1$. Hence, we only consider the case where $\beta_0 = 1$, since the entire point of taking a VES approximation, in this case, is for analytical tractability. } We can see that, as either the capacity of solar or coal dominates the market, the approximation becomes weaker. But, overall, it seems to mimic the shape of the true elasticity of substitution $e$ implied by our model of intermittency. Hence, a  VES function is a reasonable alternative to a CES function -- it better models intermittency while also maintaining parsimony.
